Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-08 content/impl.tex
uncomment labeled-expl-sup edge meaning
start and end node notation

The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
\begin{itemize}
%	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
\end{itemize}

@@

%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
\otodo{Here, you defined the output of a transformation as just G\# and an edge function. Later, you also include the lattice. Should we include the lattice here?}
Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
$\mathcal T:\ (G^\#)\to (G^\#,\,\edgefn)$
converts it into an equivalent IDE problem. We consider two transformations:
\begin{itemize}
	\item an equivalence transformation $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
  \item a correlated-call transformation $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
\end{itemize}
Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.

@@

A micro-function $f\in\lcc\to \lcc$ defines how the map from receivers to types should
be updated when an instruction is executed.
The micro-function for most kinds of instructions is the identity.
On a call to and return from a specific method $m$ called on receiver $r$,
the micro-function restricts the receiver-to-type map to map $r$ only to
types consistent with the polymorphic dispatch to method $m$.
Finally, when an instruction assigns an object of unknown type to a receiver
$r$, the corresponding micro-function updates the map to map $r$ to the
set of all types. This is made precise by the following definition:
\begin{definition}\label{def:microfn}
Given a previously fixed set $S \subseteq R$ of receivers, the micro-function $\varepsilon_S(e)$
of a supergraph edge $e$ is defined as:
                    \otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
  \begin{align}\label{eq:varepsilon}
      &\varepsilon_S(e)= \lambda m\,.\,\\
        &\begin{cases}
            m[r\to m(r)\cap \tau(s_\mathcal F,\,f)],
            &\text{\parbox{75mm}{
                if $e$ is a call-start edge, $r.c()$ is
                the call site at $n_1(e)$, $f$ is the called
                procedure with signature $s_\mathcal F$,
                and $r\in S$;}}\\[3ex]
        \parbox{30mm}{\[\begin{array}{l}
                m[r\to m(r)\cap \tau(s_\mathcal F,\,f)]\\
            [v_1\to\bot_T] \ldots [v_k\to\bot_T],
        \end{array}
        \]
        }
        &
        \text{\parbox{75mm}{
                if $e$ is an end-return edge,
                $r.c()$ is the call
                corresponding to the return node
                at $n_2(e)$,
                $f$ is the called method with
                signature $s_\mathcal F$,
                $v_1,\,\dots,\,v_k\in S$ are the local variables
                in $f$,
                and $r\in S$;}}\\
            m\left[r\to \bot_T\right],
            &\text{\parbox{75mm}{if $n_1(e)$ contains an assignment
                    for $r\in S$;}}\\
            m
                &\text{otherwise.}
        \end{cases}
  \end{align}
\end{definition}

>>>>

The meaning of an edge in the labeled exploded supergraph is the following. Let $e=((n_1,\,d_1),\,(n_2,\,d_2))\in E^\#$ be an edge in the exploded supergraph with label $f=\mathsf{EdgeFn}(e)$. Then
\begin{itemize}
	\item the fact that $d_1$ holds at node $n_1$ implies that $d_2$ holds at $n_2$;
  \item if at node $n_1$ the fact $d_1$ was mapped to a lattice element $l_1$ by an environment $Env(D,\,L)$, then the fact $d_2$ at node $n_2$ should be mapped to $f(l_1)$.
\end{itemize}

@@

%Let $P=(G^\#)$ be an IFDS problem and $Q=(G^\#,\,\edgefn)$ an IDE problem obtained by a conversion from $P$.
\otodo{Here, you defined the output of a transformation as just G\# and an edge function. Later, you also include the lattice. Should we include the lattice here?}
Let $G^\#$ be the exploded supergraph of an IFDS problem. A \emph{transformation}
$\mathcal T:\ (G^\#)\to (G^\#,\,(\top,\,\bot),\,\edgefn)$
converts it into an equivalent IDE problem with a two-point lattice. We consider two transformations:
\begin{itemize}
	\item an equivalence transformation $\transEq$ (pronounced ``t-equiv'') that generates IDE problems with the same precision as the original IFDS problem, and
  \item a correlated-call transformation $\transCC$ (pronounced ``t-c-c'') that generates IDE problems that exclude infeasible paths.
\end{itemize}
Both transformations keep the exploded supergraph $G^\#$ the same, and only generate different edge functions.
%In each case we also show how to convert the result of the generated IDE problem to a result of the original IFDS problem.

@@

A micro-function $f\in\lcc\to \lcc$ defines how the map from receivers to types should
be updated when an instruction is executed.
The micro-function for most kinds of instructions is the identity.
On a call to and return from a specific method $m$ called on receiver $r$,
the micro-function restricts the receiver-to-type map to map $r$ only to
types consistent with the polymorphic dispatch to method $m$.
Finally, when an instruction assigns an object of unknown type to a receiver
$r$, the corresponding micro-function updates the map to map $r$ to the
set of all types. This is made precise by the following definition:
\begin{definition}\label{def:microfn}
Given a previously fixed set $S \subseteq R$ of receivers, the micro-function $\varepsilon_S(e)$
of a supergraph edge $e$ is defined as:
                    \otodo{define $n_1(e)$ globally somewhere early on, and consider using a more decriptive name like src instead of $n_1$}
  \begin{align}\label{eq:varepsilon}
      &\varepsilon_S(e)= \lambda m\,.\,\\
        &\begin{cases}
            m[r\to m(r)\cap \tau(s_\mathcal F,\,f)],
            &\text{\parbox{75mm}{
                if $e$ is a call-start edge, $r.c()$ is
                the call site at $\src e$, $f$ is the called
                procedure with signature $s_\mathcal F$,
                and $r\in S$;}}\\[3ex]
        \parbox{30mm}{\[\begin{array}{l}
                m[r\to m(r)\cap \tau(s_\mathcal F,\,f)]\\
            [v_1\to\bot_T] \ldots [v_k\to\bot_T],
        \end{array}
        \]
        }
        &
        \text{\parbox{75mm}{
                if $e$ is an end-return edge,
                $r.c()$ is the call
                corresponding to the return node
                at $\target e$,
                $f$ is the called method with
                signature $s_\mathcal F$,
                $v_1,\,\dots,\,v_k\in S$ are the local variables
                in $f$,
                and $r\in S$;}}\\
            m\left[r\to \bot_T\right],
            &\text{\parbox{75mm}{if $\src e$ contains an assignment
                    for $r\in S$;}}\\
            m
                &\text{otherwise.}
        \end{cases}
  \end{align}
\end{definition}
